CTA Proposal:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe

### 2021-03-12 Phys 311/CTA/Paper/paper.tex
Content

\title{CTA Proposal:\\SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}

@@

In the past decade efforts such as the Sloan Digital Sky Survey (SDSS) have uncovered a plethora of very dim dwarf spheroidal
(dSph) galaxies and ultra faint dwarfs. These dSph and ultra faint dwarfs have total luminosities in the range of
\(10^{5} L_{\odot} \lesssim L \lesssim 10^{7} L_{\odot}\) and \(L \lesssim 10^5 L_{\odot}\), respectively, which contain
stars with [Fe/H] values of $\sim -2.5$. With the use of medium resolution spectroscopy scientists recently uncovered a
moderate population of super low metal stars with [Fe/H] values $< -3.0$ within ultra fain dwarfs. Within the same systems
scientists did not find any stars with [Fe/H] $> -1.0$. In this population one galaxy, SEGUE 1, stood out from the rest. 
SEGUE 1's population of stars show increasing metallicity, in the form of $\alpha$-elements, but do not exhibit decreasing
[$\alpha$/Fe] ratios. 
This would indicate that the star formation phase in SEGUE 1 occurred before most, if not all, Type Ia supernovae events. This
also indicates that there was likely only one star formation phase within the galaxy.

@@

The authors of this paper made new spectrography measurements of six stars within SEGUE 1 using the Magellan/MIKE and Keck/HIRES
spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
stars that were chosen were the brightest stars in SEGUE 1 which allowed for high resolution spectrography. Using the spectrographs
the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, and neutron-capture elements. The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
The parameters for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
noise ratio (S/N) was only moderate with values between 20 and 50

@@

With the high resolution spectrograph data the authors were able to extrapolate the abundances of the various elements inside the stars.
In figure 1 the authors plotted the spectra of the 6 stars compared to two other known stars, the ultra low metal $CD -38^{\circ}245$
and the very bright, and much younger, Arcturus.

In the three lowest metallicity stars (The top 3 blue lines) the abundance of iron (both Fe I and Fe II) is mostly indistinguishable
from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing
iron abundance and increasing metallicity, indicated by the appearance of more spectral lines. This indicated that there was at most
one or maybe two Type Ia supernova that enriched SEGUE. This
contrasts the trend found in younger galaxies where there would be a clear trend in increasing metallicity and increasing
iron abundance in the stellar population as they evolve alongside energetic supernovae events.

Other indications of the age of SEGUE include enhanced [$\alpha$/Fe] values found in all it's stars that are consistent with the birth 
cloud, and the low abundance of neutron-capture
elements. The consistent [$\alpha$/Fe] values in SEGUE 1 stars suggest that there were no energetic supernovae events that enriched
the birth gas cloud during the star formation events. The low abundance of neutron-capture elements in SEGUE's non-binary stars,
which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.

@@

% End of file `sample63.tex'.

>>>>

\title{CTA Proposal:\\SEGUE-1: An Unevolved Fossil Galaxy from the Early Universe}

@@

In the past decade efforts such as the Sloan Digital Sky Survey (SDSS) have uncovered a plethora of very dim dwarf spheroidal
(dSph) galaxies and ultra faint dwarfs. These dSph and ultra faint dwarfs have total luminosities in the range of
\(10^{5} L_{\odot} \lesssim L \lesssim 10^{7} L_{\odot}\) and \(L \lesssim 10^5 L_{\odot}\), respectively, which contain
stars with [Fe/H] values of $\sim -2.5$. With the use of medium resolution spectroscopy scientists recently uncovered a
moderate population of super low metal stars with [Fe/H] values $< -3.0$ within ultra fain dwarfs. Within the same systems
scientists did not find any stars with [Fe/H] $> -1.0$. In this population one galaxy, SEGUE-1, stood out from the rest. 
SEGUE-1's population of stars show increasing metallicity, in the form of $\alpha$-elements, but do not exhibit decreasing
[$\alpha$/Fe] ratios. 
This would indicate that the star formation phase in SEGUE-1 occurred before most, if not all, Type Ia supernovae events. This
also indicates that there was likely only one star formation phase within the galaxy.

@@

The authors of this paper made new spectrography measurements of six stars within SEGUE-1 using the Magellan/MIKE and Keck/HIRES
spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
stars that were chosen were the brightest stars in SEGUE-1 which allowed for high resolution spectrography. Using the spectrographs
the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, and neutron-capture elements.
The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
The parameters for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
noise ratio (S/N) was only moderate with values between 20 and 50

@@

With the high resolution spectrograph data the authors were able to extrapolate the abundances of the various elements inside the stars.
In figure 1 the authors plotted the spectra of the 6 stars compared to two other known stars, the ultra low metal $CD -38^{\circ}245$
and the very bright, and much younger, Arcturus. The plots are listed in ascending order of metallicity from top to bottom.

%% Figure of spectra

In the three lowest metallicity stars (The top 3 blue lines) the abundance of iron (both Fe I and Fe II) is mostly indistinguishable
from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing
iron abundance and increasing metallicity, indicated by the appearance of more spectral lines as the metallicity increases.
This indicated that there was at most one or maybe two Type Ia supernova that enriched SEGUE-1's birth cloud. This
contrasts the trend found in younger galaxies where there would be a clear trend in increasing metallicity and increasing
iron abundance in the stellar population as they evolve alongside energetic supernovae events.

%% Fig of [X/Fe] vs [Fe/H]

Another indication of SEGUE-1's age is the enhanced [$\alpha$/Fe] values found in all the measured stars that are consistent with each other
and the initial birth cloud. Figure 3 shows enrichment behavior plots, [Fe/H] vs. [$\alpha$/Fe], for MW Halo stars, classical dSph galaxy stars, and SEGUE-1 stars.
The top plot in fig. 3 shows the general trend of how classical dSph galaxies and MW Halo stars will appear on the enrichment behavior plot.
The middle plot shows the spread of MW Halo stars which have a plateau in the [$\alpha$/Fe] until [Fe/H] $\approx -1$ at which point
the [$\alpha$/Fe] approaches 0 where [Fe/H] is almost at 0. The bottom plot of fig. 3 shows the enrichment behavior plot for dSph galaxy
stars (small black circles), the measured stars from SEGUE-1 (large red filled in circles from this article, and red crosshair from
previous papers), and some other candidate stars (blue square, green circles, and magenta circles). In this bottom plot we can see that
the classical dSph stars and some of the other candidate stars have a plateau but do slope down towards the [$\alpha$/Fe] = 0 line.
On the other hand, the 6 measured stars from SEGUE-1 all reside around the [$\alpha$/Fe] = 0.5 line, even past the point where MW
Halo starts to slope down on the [Fe/H] axis. The consistent [$\alpha$/Fe] values in SEGUE-1 stars suggest that after the initial
enrichment of the birth cloud there were no other enrichment events, such as type Ia supernovae, in SEGUE-1.

%% Fig of Enrichment Behavior

The final indicator of SEGUE-1's old age is the low abundance of neutron-capture elements in SEGUE's non-binary system stars,
which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.

@@
